US Korea Exchange Rates \\ STA206 Final Project

### 2014-12-07 paper.tex
us debt plot
following paper structure

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    {\Large Assignment 1}\\
    \bigskip
    \hrule
    \medskip
    Clark Fitzgerald\\
    Stats 123
\end{center}

\section*{Makefiles}

Originally designed for compiling large software projects, Makefiles can automate the dependencies between data analysis steps, enabling \textbf{reproducible research}.\footnote{For more on reproducible research, check out the chapter on Open Source Scientific Practice by K. Jarrod Millman and Fernando Perez available at \url{https://osf.io/h9gsd/}.}

\begin{description}
    \item[Statistics-] So hot right now.
    \begin{enumerate}
        \item This is a nested list.
        \item We are shooting for highly nested stuff here.
    \end{enumerate}
    \item[Mathematics-] Always classic.
\end{description}

\vspace{0.3in}

\subsubsection*{R graphics}

Display equations:

\[
    f(x) = x^2 + 5x + \pi
\]

Inline equation $\sum x$, and so on.

You can generate simulated data with R or Python.

\section{R for Graphics}

Here is some R code.

Which generates the corresponding plot:

\centerline{\includegraphics{correlation.pdf}}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{US Korea Exchange Rates \\ STA206 Final Project}
\date{December 15, 2014}
\author{Clark Fitzgerald clarkfitzg@gmail.com \\ 
        Amy Kim atykim@ucdavis.edu}

\maketitle

\begin{abstract}
    We analyze the exchange rate between the United States and South Korea
    using monthly country level economic data.
\end{abstract}

\section{Introduction}

\section{Methods and Results}

Figure~\ref{fig:correlation} shows a histogram of all the pairwise sample
correlations.

Figure~\ref{fig:na_plot_KOR} shows the variables which were interpolated.

\section{Conclusions and Discussion}

\newpage
\section{Appendix}

\listoffigures

\begin{figure}
  \centering
    \includegraphics{correlation.pdf}
  \caption{Histogram of all pairwise sample correlations.}
  \label{fig:correlation}
\end{figure}

\begin{figure}
  \centering
    \includegraphics{na_plot_KOR.pdf}
  \caption{Scaled variables with NA values.}
  \label{fig:na_plot_KOR}
\end{figure}
